Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-23 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
renamed files
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\title{Applying automated verification to optimal sizing of stand-alone solar photovoltaic systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Alessandro Trindade}
\IEEEauthorblockA{\textit{Electricity Department} \\
\textit{Federal University of Amazonas}\\
Manaus, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Lucas Cordeiro}
\IEEEauthorblockA{\textit{School of Computer Science} \\
\textit{The University of Manchester}\\
Manchester, England \\
lucas.cordeiro@@manchester.ac.uk }
}

@@

\begin{abstract}
Currently around 1 billion of people do not have electrical energy. Energy poverty alleviation has become an important political issue. Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. Particular attention is given to use renewables and stand-alone solar photovoltaic (PV) systems. Validation tools are available to evaluate PV designs, but they are mainly based on simulations that do not cover all aspects of the design space. The use of automated verification in PV systems is a recent subject with a few initiatives. Here we create an algorithm and use four state-of-art automated verification techniques to optimize the sizing of a solar photovoltaic system, where commercial equipment data is part of the specification of the code. Furthermore, the technical solution is conjugated with the financial analysis of the sizing obtained. The proposal is unprecedented and interesting to streamline the design and analysis of photovoltaic solar systems projects.Experimental results show promising results, even with state explosion and time to computing issues not solved yet.
\end{abstract}

>>>>

\title{Applying Automated Verification to Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Alessandro Trindade}
\IEEEauthorblockA{\textit{Electricity Department} \\
\textit{Federal University of Amazonas}\\
Manaus, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{Lucas Cordeiro}
\IEEEauthorblockA{\textit{School of Computer Science} \\
\textit{University of Manchester}\\
Manchester, England \\
lucas.cordeiro@@manchester.ac.uk }
}

@@

\begin{abstract}
Software verification has experienced significant progress over the last two decades. Currently, there exist various software verifies that are able to solve intricate real-world problems, e.g., to design and verify renewable and stand-alone solar photovoltaic (PV) systems. 
Currently around $1$ billion of people do not have electrical energy; energy poverty alleviation has become an important political issue. 
%Several initiatives and policies have been proposed to deal with poor access to sources of energy in many developing countries. 
Particular attention is given to renewables and PV systems. Unfortunately, existing tools available to evaluate PV designs are mainly based on simulations that do not cover all aspects of the design space. 
The use of automated verification in PV systems is a recent subject with only a few initiatives. 
Here we develop an optimization algorithm and report its preliminary results using four state-of-art software verifiers to optimize the sizing of a PV system, where commercial equipment data is part of the specification and the technical solution is conjugated with the financial analysis of the obtained sizing. 
Our proposal is unprecedented and interesting to streamline the design and analysis of PV systems. Experimental results show that \textcolor{red}{we should describe here a summary of the results}.
\end{abstract}
